\documentclass{article}
\usepackage[hidelinks]{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\newcommand{\tc}{t_\text{c}}

\begin{document}

\section*{Advent of Code - Day 6}
While reading the task of Advent of Code Day 6\footnote{\url{https://adventofcode.com/2023/day/6}}, 
the reader may swiftly realize that this problem is obviously nothing else then an inequality of a quadratic equation.
Let $t_0$ be the time a race $r$ takes and $d_0$ the distance one has to overcome. 
By holding down the button for a time $\tc$ the boat accelerates without changing its position with unit acceleration $a = 1\text{m}/\text{s}$.
Thus, the velocity after a charging time of $\tc$ is just $v = a \cdot \tc = \tc$\footnote{If not stated otherwise, all lengths are in millimeter and times in milliseconds.}.
Using this we can find the relation 
\begin{equation}
    d_0 < t_0\cdot \tc -\tc^2
    \label{constraint}
\end{equation}
Solving this inequality for $\tc$ yields the time-interval that one can target in order to win the race. 
The solution is formally given by 
\begin{equation}
    (\tc-t_+)(\tc-t_-) < 0
\end{equation}
with 
\begin{equation}
        t_\pm = \frac{t_0}{2} \pm \sqrt{\frac{t_0^2}{4} - d_0}.
        \label{eq:time_interval}
\end{equation}
Since $t_+>t_-$ there is only one case for which this inequality holds, namely $\tc \in I:=(t_-, t_+)$.
However since the problem is formulated for times $\tc \in \mathbb{N}$, we have to round the interval $I$ to the nearest integer.
Define $I_N:=(\lceil t_-\rceil, \lfloor t_+ \rfloor)$. All $\tc \in I_N$ are valid solutions to the problem.
The number of possible strategies $s$ for a race $r$ is given by the cardinality of $I_N$, i.e. 
\begin{equation}
    s=|I_N| = \lfloor t_+ \rfloor - \lceil t_- \rceil + 1.
    \label{eq:number_of_strategies}
\end{equation}
\subsection*{Problem 1}
The input for the first problem was given as displayed in Table \ref{tab:time_distance}.
\begin{table}[ht]
    \centering
    \begin{tabular}{ccc}
        \textbf{Race} $r$ & \textbf{Time} $t_0$& \textbf{Distance} $d_0$\\
        1 & 54 & 302 \\
        2 & 94 & 1476 \\
        3 & 65 & 1029 \\
        4 & 92 & 1404 \\
    \end{tabular}
    \caption{Time and Distance}
    \label{tab:time_distance}
\end{table}
Using the equations \ref{eq:time_interval} together with \ref{eq:number_of_strategies} yields the following results:
\begin{table}[ht]
    \centering
    \begin{tabular}{cccc}
        \textbf{Race} $r$ & \textbf{$t_+$} & \textbf{$t_-$} & \textbf{$s$}\\
        1 & 47.66 & 6.34 & 41\\
        2 & 74.07 & 19.93 & 55\\
        3 & 37.72 & 27.30 & 10\\
        4 & 72.68 & 19.32 & 53\\
    \end{tabular}
    \caption{Time and Distance. Interval bounds are rounded to second decimal place.}
    \label{tab:day1_results}
\end{table}
Multiplying all the results $s$ together yields the number $1195150$, which is the correct results.
\newpage
\subsection*{Problem 2}
This input was just one race with time $t_0 = 54946592$ and distance $d_0 = 302147610291404$. This results in 
\begin{equation*}
    t_+ = 48748501.82302818 \quad,\quad t_- = 6198090.176971823 \quad \text{and} \quad s = 42550411.
\end{equation*}
\end{document}
